### 2024-08-10 machine-learning.qmd
20240809 - updates

@@

seasonalData_subset_imp <- missForest::missForest(
  seasonalData_subset %>% select(ageCentered20, ageCentered20Quadratic, fantasyPoints_lag) %>% data.frame,
  verbose = TRUE,
  mtry = 100,
  parallelize = "forests")
```

@@

```{r}
smerf <- LongituRF::MERF(
  X = seasonalData_subset_imp$ximp[,c("ageCentered20")] %>% as.matrix(),
  Y = seasonalData_subset_imp$ximp[,c("fantasyPoints_lag")],
  Z = seasonalData_subset_imp$ximp[,c("ageCentered20")] %>% as.matrix(),
  id = seasonalData_subset$gsis_id,
  time = seasonalData_subset_imp$ximp[,c("ageCentered20")] %>% as.matrix(),
  mtry = 2,
  ntree = 500,
  sto = "BM")

>>>>

### Split into Test and Training Data {#sec-splitTestTraining}

@@

seasonalData_subset_imp <- missForest::missForest(
  seasonalData_subset %>% select(ageCentered20, ageCentered20Quadratic, years_of_experience, position_group, fantasyPoints_lag) %>% data.frame,
  verbose = TRUE,
  mtry = 100,
  parallelize = "forests")
```

@@

```{r}
smerf <- LongituRF::MERF(
  X = seasonalData_subset_imp$ximp[,c("position_group")] %>% as.matrix(),
  Y = seasonalData_subset_imp$ximp[,c("fantasyPoints_lag")],
  Z = seasonalData_subset_imp$ximp[,c("years_of_experience")] %>% as.matrix(),
  id = seasonalData_subset$gsis_id,
  time = seasonalData_subset_imp$ximp[,c("ageCentered20")] %>% as.matrix(),
  mtry = 2,
  ntree = 500,
  sto = "BM")
